The evolution of the transcriptome of mammalian placentas

### 2016-11-14 manuscript/manuscript.Rnw
it's actin y
remove discussion of brain size

\subsubsection{Invasion: EGF and Auxin Y in the Core Placenta}

@@

\clearpage

@@

\subsubsection{Invasion: EGF and Auxin Y in the Core Placenta}

@@

The \human placenta is distinctive from many other primates in that it
possesses a deeply invasive trophoblast that penetrates the inner
myometrium of the uterus
\cite{Carter.ea2011:Evolutionofinvasiveplacentation}. It is
hypothesized that this feature is related to the increased demand for
resources by the developing fetus to feed the expanded size of the
human brain
\cite{Carter.ea2011:Evolutionofinvasiveplacentation,Robillard.ea2002:Evolutionaryadaptationstopre-eclampsiaeclampsia}.
\human have the largest brain in terms of relative size and this
differs markedly from closely related apes
\cite{Boddy.ea2012:Comparativeanalysisofencephalization}. Deep
penetration of the myometrium occurs in chimpanzees and gorillas, but
this penetration may be accelerated in humans
\cite{Carter.ea2011:Evolutionofinvasiveplacentation}.

>>>>

Another annexin which is highly expressed in the core placenta is
\textit{ANXA5}, a gene which was originally identified as

\subsubsection{Invasion: EGF and Actin Y in the Core Placenta}

@@

@@

\subsubsection{Invasion: EGF and Actin Y in the Core Placenta}

@@

The \human placenta is distinctive from many other primates in that it
possesses a deeply invasive trophoblast that penetrates the inner
myometrium of the uterus
\cite{Carter.ea2011:Evolutionofinvasiveplacentation}. It is
hypothesized that this feature is related to the increased demand for
resources by the developing fetus to feed the expanded size of the
human brain
\cite{Carter.ea2011:Evolutionofinvasiveplacentation,Robillard.ea2002:Evolutionaryadaptationstopre-eclampsiaeclampsia}.
